Weak interspecific interactions in a sagebrush steppe: evidence from observations, models, and experiments

### 2017-05-12 removals/manuscript/cover.tex
Incorporated Ellner and Hooker edits to removal manuscript

We are hereby submitting our manuscript, ``Weak interspecific interactions in a sagebrush steppe: evidence from observations, models, and experiments''
for publication as a Standard Paper in the Journal of Ecology.

@@

Overall, the results of our experiment increase our confidence that the structure and dynamics of this plant community are determined more by variation in intraspecific interactions than by strong interspecific competition for resources. We expect this conclusion may surprise a broad audience of plant ecologists accustomed to studies emphasizing the importance of interspecific competition.

@@

\bibliographystyle{Ecology}
\bibliography{RemovalRefs}

\newpage

@@

Adler, P.B., Dalgleish, H.J. \& Ellner, S.P. (2012) Forecasting plant community impacts of climate variability and change: when do competitive interactions matter? Journal of Ecology, 100, 478-487.

Adler, P.B., Ellner, S.P. \& Levine, J.M. (2010) Coexistence of perennial plants: an embarrassment of niches. Ecology Letters, 13, 1019-1029.

Chu, C. \& Adler, P.B. (2015) Large niche differences emerge at the recruitment stage to stabilize grassland coexistence. Ecological Monographs, 85, 373-392.

>>>>

Please consider our manuscript, ``Weak interspecific interactions in a sagebrush steppe: evidence from observations, models, and experiments''
for publication as an Article in \textit{Ecology}.

@@

Overall, the results of our experiment increase our confidence that the structure and dynamics of this plant community are determined more by variation in intraspecific interactions than by strong interspecific competition for resources. We expect this conclusion may surprise a broad audience of plant ecologists accustomed to studies emphasizing the importance of interspecific competition. Our results also support the use of observational data to build multispecies population models and explore community dynamics.

@@

@@

Adler, P.B., Dalgleish, H.J. and Ellner, S.P. 2012. Forecasting plant community impacts of climate variability and change: when do competitive interactions matter? Journal of Ecology 100: 478-487.

Adler, P.B., Ellner, S.P. and Levine, J.M. 2010. Coexistence of perennial plants: an embarrassment of niches. Ecology Letters 13: 1019-1029.

Chu, C. and Adler, P.B. 2015. Large niche differences emerge at the recruitment stage to stabilize grassland coexistence. Ecological Monographs 85: 373-392.
